\ecvsection{Work experience}

\ecvitem{Dates}{\bfseries{July 2013 - May 2015}}

\ecvitem{Occupation or position held}{Ruby on Rails Developer}

\ecvitem{Main activities and responsibilities}{Design, develop and maintain Ruby
  and Ruby on Rails web applications.}

\ecvitem{Name and address of employer}{\textbf{Shtrak BG LLC}, 5 Debar st.,
Varna, Bulgaria}

\\

\ecvitem{Dates}{\bfseries{May 2015 - October 2016}}

\ecvitem{Occupation or position held}{Founder, Ruby on Rails Developer}

\ecvitem{Main activities and responsibilities}{Design, development and support
  of the ERP system used to simplify food production, and the front-facing sales
  and deliveries system of the start-up.}

\ecvitem{Name and address of employer}{\textbf{CoKitchen (now defunct)}, 4 Gourko st., Sofia,
Bulgaria}

\\

\ecvitem{Dates}{\bfseries{November 2016 - December 2018}}

\ecvitem{Occupation or position held}{Ruby on Rails Developer}

\ecvitem{Main activities and responsibilities}{Development of the human resources
management system at the core of the start-up.}

\ecvitem{Name and address of employer}{\textbf{Domestina}, 28, Rilski Ezera st.,
Sofia, Bulgaria}

\\

\ecvitem{Dates}{\bfseries{January 2019 - October 2019}}

\ecvitem{Occupation or position held}{Senior Software Engineer}

\ecvitem{Main activities and responsibilities}{Maintenance and support of the
Skrill digital wallet. My responsibilities included keeping the Rails-based
merchant-facing project in operational state as it was phased out in favour of a
Java-based solution.}

\ecvitem{Name and address of employer}{\textbf{Paysafe Bulgaria}, 90, Tsarigradsko Shose blvd.,
Sofia, Bulgaria}

\\

\ecvitem{Dates}{\bfseries{May 2018 - December 2019}}

\ecvitem{Occupation or position held}{Consultant}

\ecvitem{Main activities and responsibilities}{Provide expert technical and software engineering
advice to the project managers responsible for the then-ongoing projects for
developing a new \textbf{open data portal}, a \textbf{platform for requesting access to
public data} and an enhanced \textbf{public consultations portal}.}

\ecvitem{Name and address of employer}{\textbf{Administration of the Council of Ministers}, 1, Doundukov blvd.,
Sofia, Bulgaria}


\\

\ecvitem{Dates}{\bfseries{October 2019 - current}}

\ecvitem{Occupation or position held}{Senior Software Engineer}

\ecvitem{Main activities and responsibilities}{Development of the Acronis Cyber
Files cloud-based file sharing solution. Responsibilities included mostly
refactoring and optimising legacy code (Ruby, SQL) that had been engineered for
low scale on-premise use. At the end of my tenure I worked on the product's
migration to Kubernetes.}

\ecvitem{Name and address of employer}{\textbf{Acronis Bulgaria}, NV Tower, G.M. Dimitrov Blvd 59, 1700 Studentski Kompleks, Sofia, Bulgaria}
